Evaluating FAIR Digital Object and Linked Data as distributed object systems

### 2023-06-26 latex/main.tex
avoid _ in bib

From this mapping\footnote{An equivalent SKOS mapping \autocite{w3-skos-primer} is provided as part of the \href{https://w3id.org/ro/doi/10.5281/zenodo.8075229}{RO-Crate for this article} \autocite{stian_soiland_reyes_2023_8075230}.} we can identify the conceptual similarities between DOIP and HTTP, often with common terminology. Notable are that neither DOIP or HTTP have strong support for transactions (explored further \vpageref{sec:middleware}), as well that HTTP has poor direct support for processes, as the Web is primarily stateless by design.

>>>>

From this mapping\footnote{An equivalent SKOS mapping \autocite{w3-skos-primer} is provided as part of the \href{https://w3id.org/ro/doi/10.5281/zenodo.8075229}{RO-Crate for this article} \autocite{soilandreyes2023}.} we can identify the conceptual similarities between DOIP and HTTP, often with common terminology. Notable are that neither DOIP or HTTP have strong support for transactions (explored further \vpageref{sec:middleware}), as well that HTTP has poor direct support for processes, as the Web is primarily stateless by design.
